PyPy's Approach to \\ Implementing Dynamic Languages \\ Using a Tracing JIT Compiler

### 2011-02-07 talk/ibm-feb-2011/talk.tex
replace pseudo-code by diagram

\begin{frame}[containsverbatim, plain]
  \frametitle{Method-Based JITs and Dispatching Dependencies}
\begin{verbatim}
    if isinstance(a, Integer):
        if isinstance(b, Integer):
            x = Integer(<perform int addition>)
        else:
            x = Float(<perform float addition>)
    else:
        x = Float(<perform float addition>)
    # x can be Float or Integer here
    if isinstance(x, Integer):
        if isinstance(c, Integer):
            r = Integer(<perform int addition>)
        else:
            r = Float(<perform float addition>)
    else:
        r = Float(<perform float addition>)
\end{verbatim}
\end{frame}

>>>>

\begin{frame}[containsverbatim, plain]
  \frametitle{Method-Based JITs and Dispatching Dependencies}
  \includegraphics[scale=0.5]{figures/add1.pdf}
%\begin{verbatim}
%    if (isinstance(a, Integer) and
%            isinstance(b, Integer)):
%        x = Integer(<perform int addition>)
%    else:
%        x = Float(<perform float addition>)
%
%    # x can be Float or Integer here
%
%    if (isinstance(x, Integer) and
%            isinstance(c, Integer)):
%        r = Integer(<perform int addition>)
%    else:
%        r = Float(<perform float addition>)
%\end{verbatim}
\end{frame}

\begin{frame}[containsverbatim, plain]
  \frametitle{Method-Based JITs and Dispatching Dependencies}
  \includegraphics[scale=0.39]{figures/add2.pdf}
\end{frame}

\begin{frame}[containsverbatim, plain]
  \frametitle{Method-Based JITs and Dispatching Dependencies}
  \includegraphics[scale=0.41]{figures/add_fast.pdf}
\end{frame}
